<!-- # --- -->
<!-- # title: "Find me best beer" -->
<!-- # author: Ravi Kothari   -->
<!-- # output: ioslides_presentation -->
<!-- #  -->
<!-- # .codefont pre { -->
<!-- #  -->
<!-- #     font-size: 12px; -->
<!-- #     line-height: 10px; -->
<!-- # } -->
  
---
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction


The final project for DATA 607 aims to find the best breweries in a particular area based on their ratings and their beer ratings. This project scrapes the data from beeradvocate website and then plots them on the map.


## Motivation


The Motivation behind this project was to find the best beer in my area and also to visualize the breweries and see which areas has more high rated brewries when plotted on the map.

## Overview of data gathered


The app first takes the beeradvocate URL as an input and then scrape it to get the following characteristic of the brewery and beer.

- Brewery Name.
- Brewery ratings.
- No. of reviews.
- Average beer rating for that particular brewery.
- No. of beers in that brewery.
- Address of the brewery.


## Code to scrape the Data.{.smaller}



To scrape the data we used rvest package, the code below loops through all the result pages and gather the brewery data. After that we converted it to a dataframe for cleaning and transforming.

```{r, echo=TRUE, message=FALSE}

library(RCurl)
library(XML)
library(rvest)
library(knitr)
library(dplyr)
library(stringr)
library(devtools)


#parse the URL

theURL <- "https://www.beeradvocate.com/place/list/?start=0&&c_id=US&s_id=CA&brewery=Y&sort=name"
pageURL <- vector(mode="character", length=0)
brewery <- vector(mode="character", length=0)
final <- vector(mode="character", length=0)
final_add <- vector(mode="character", length=0)
brewery_add <- vector(mode="character", length=0)


scrape_brewery_links <- function(page_data){
  brewery <- page_data %>%
    html_nodes(xpath='//*[contains(concat( " ", @class, " " ), concat( " ", "hr_bottom_light", " " ))]//b | //a//b') %>%
    html_text()
  brewery <- brewery[-1]
  
  return(brewery)
}

scrape_brewery_address <- function(page_data){
  brewery <- page_data %>%
    html_nodes(xpath='//*[contains(concat( " ", @class, " " ), concat( " ", "hr_bottom_dark", " " )) and (((count(preceding-sibling::*) + 1) = 1) and parent::*)]') %>%
    html_text()
  #brewery <- brewery[-1]
  #output <- matrix(unlist(brewery), ncol = 5, byrow = TRUE)
  return(brewery)
}

#get the total number of pages

pages <- read_html(theURL) %>%
  html_nodes(xpath='//span//b[(((count(preceding-sibling::*) + 1) = 1) and parent::*)]') %>%
  html_text()

# regex to convert it into numbers
results <- str_extract(pages,"of \\d+")
results <- as.numeric(str_extract(results,"\\d+"))

# need this conversion for the website and how they name the page numbers.
page_no = results/20;
page_no = ceiling(page_no) #number of pages
page_no_url = page_no*20 #for URL string

# Loop through all the pages :
loop_URL <- "https://www.beeradvocate.com/place/list/?start="
for (i in c(1:page_no)){
  Sys.sleep(1)
  page_no_url = (i-1)*20
  pageURL[i] <- paste(loop_URL,page_no_url,"&c_id=US&s_id=CA&brewery=Y&sort=name",sep = "")
  page_data <- read_html(pageURL[i])
  brewery = scrape_brewery_links(page_data)
  final = append(final,brewery)
  remove(brewery)
  brewery_add = scrape_brewery_address(page_data)
  final_add = append(final_add,brewery_add)
  remove(brewery_add)
}

brewery_mat <- matrix(unlist(final), ncol = 5, byrow = TRUE)
brewery_final <- cbind(brewery_mat,final_add)
beer_df <- as.data.frame(brewery_final)


```


## The results after scraping



```{r, echo=FALSE}

head(beer_df)

```

## Cleansing the data {.smaller}


After scraping we need to clean and reformat the data.

```{r, echo=TRUE, message=FALSE, warning=FALSE}
# change the column names
colnames(beer_df) <- c("brewery_name", "brewery_rating", "number_of_reviews", "beer_avg", "number_of_beers", "address")

# get our missing values as NA
beer_df[beer_df == "-"] = NA

# clean up some of the columns and remove extra data
beer_df$address <- as.character(beer_df$address) # change into character data type

library(stringr)
beer_df$phone_number <- str_extract_all(beer_df$address, "\\(?\\d{3}\\)?[.-]? *\\d{3}[.-]? *[.-]?\\d{4}")
beer_df$phone_number[beer_df$phone_number == "character(0)"] = NA

# remove the phone number tag from the address field for geocoding
beer_df$address <- gsub("\\(?\\d{3}\\)?[.-]? *\\d{3}[.-]? *[.-]?\\d{4}", "", beer_df$address)
beer_df$address <- gsub("United States", " United States", beer_df$address)
beer_df$address <- gsub('([[:lower:]])([[:upper:]])', '\\1 \\2',beer_df$address)
beer_df$address <- gsub('([[:digit:]])([[:upper:]])', '\\1 \\2',beer_df$address)
beer_df$address <- gsub('(\\.)([[:upper:]])', '\\1 \\2',beer_df$address)
beer_df$address <- gsub('([[:upper:]])([[:upper:]])', '\\1 \\2',beer_df$address)

# change the factor for average beer rating into a numeric

beer_df$beer_avg <- as.numeric(levels(beer_df$beer_avg))[beer_df$beer_avg]
beer_df$brewery_rating <- as.numeric(levels(beer_df$brewery_rating))[beer_df$brewery_rating]
beer_df$number_of_reviews <- as.numeric(beer_df$number_of_reviews)

top_beer <-     beer_df %>%
  filter(!is.na(number_of_reviews)) %>%
  filter(!is.na(beer_avg)) %>%
  filter(number_of_reviews >= 100 | beer_avg >= 4) %>%
  arrange(desc(beer_avg),desc(number_of_reviews))

top_brewery <-     beer_df %>%
  filter(!is.na(number_of_reviews)) %>%
  filter(!is.na(brewery_rating)) %>%
  filter(number_of_reviews >= 50 & brewery_rating >= 4) %>%
  arrange(desc(brewery_rating),desc(number_of_reviews))

```

## Create location cordinates{.smaller}


```{r, echo=TRUE, message=FALSE, warning=FALSE}

library(htmlwidgets)
library(leaflet)
library(ggmap)
library(dplyr)
library(RColorBrewer)

# This function geocodes a location (find latitude and longitude) using the Google Maps API
geo <- geocode(location = top_beer$address, output="latlon", source="google")
geo2 <- geocode(location = top_brewery$address, output="latlon", source="google")

# add those coordinates to our dataset
top_beer$lon <- geo$lon
top_beer$lat <- geo$lat

# add those coordinates to our dataset
top_brewery$lon <- geo2$lon
top_brewery$lat <- geo2$lat



```


## Results


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# create the pop-up info
top_beer$pop_up_content <- paste(sep = "<br/>", 
                                    "<b><a href='", top_beer$brewery_name, "'>", top_beer$brewery_name, "</a></b>", top_beer$address,
                                    top_beer$phone_number, paste("Average beer rating: ", top_beer$beer_avg,"/5.0"))

# add colors corresponding to the average beer ratings  
pal <- colorNumeric(palette = "YlOrRd", top_beer$beer_avg, n = 5)


leaflet(data = top_beer) %>% 
  addTiles() %>%
  setView(lng =-119.417931, lat=36.778259, zoom = 6) %>%
  addMarkers(lng = top_beer$lon[!is.na(top_beer$lon)], 
             lat = top_beer$lat[!is.na(top_beer$lat)], popup = ~as.character(pop_up_content))
```

## Results

Mapping of breweries based on their beer ratings.

```{r, echo=FALSE,message=FALSE,warning=FALSE}

leaflet(top_beer) %>% 
  addTiles('http://{s}.basemaps.cartocdn.com/dark_all/{z}/{x}/{y}.png', 
                              attribution='Map tiles by <a href="http://stamen.com">Stamen Design</a>, <a href="http://creativecommons.org/licenses/by/3.0">CC BY 3.0</a> &mdash; Map data &copy; <a href="http://www.openstreetmap.org/copyright">OpenStreetMap</a>') %>%
  setView(-119.417931, 36.778259, zoom = 5) %>% 
  addCircleMarkers(lng = top_beer$lon[!is.na(top_beer$lon)], 
                 lat = top_beer$lat[!is.na(top_beer$lat)], radius=5, 
                 stroke = TRUE, fillOpacity = 1,
                 popup = ~as.character(pop_up_content), 
                 color = ~pal(beer_avg)) %>% 
  addLegend("topright", pal = pal, values = top_beer$beer_avg,
                title = "Average Beer Ratings at Brewery",
                opacity = 1)

```

## Results

Mapping of the breweries based on the brewery ratings.


```{r, echo=FALSE,message=FALSE,warning=FALSE}

top_brewery$pop_up_content <- paste(sep = "<br/>", 
                                 "<b><a href='", top_beer$brewery_name, "'>", top_beer$brewery_name, "</a></b>", top_beer$address,
                                 top_beer$phone_number, paste("Average brewery rating: ", top_brewery$brewery_rating,"/5.0"))

pal <- colorNumeric(palette = "YlOrRd", top_brewery$brewery_rating)

leaflet(data = top_brewery) %>% 
  addTiles() %>%
  setView(lng =-119.417931, lat=36.778259, zoom = 6) %>% 
  addCircleMarkers(lng = top_brewery$lon[!is.na(top_brewery$lon)], 
                   lat = top_brewery$lat[!is.na(top_brewery$lat)], popup = ~as.character(pop_up_content), color = ~pal(top_beer$brewery_rating)) %>%
  addLegend("topright", pal = pal, values = top_brewery$brewery_rating,
            title = "Brewery Ratings",
            opacity = 1)
```

## Challenges and lessons learned

Some of the challenges faced were:

- Address formatting,
- Due to which it was calculating wrong coordinates.
- Also something new I learned in this project is about leaflet package and ioslides.

## References

- http://stackoverflow.com/questions/3418128/how-to-convert-a-factor-to-an-integer-numeric-without-a-loss-of-information
- https://github.com/parryc/beer-advocate-api
- https://www.r-bloggers.com/the-leaflet-package-for-online-mapping-in-r/
- http://rmarkdown.rstudio.com/ioslides_presentation_format.html



